LAGOS lake depth

### 2019-12-28 figures/00_maps.Rmd
cleanup

```{r 00_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(maxdepth_class = smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, Inf)))
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
hu4_focal     <- st_crop(st_transform(
  lwgeom::st_make_valid(hu4_focal), st_crs(study_bbox)), 
  study_bbox)

@@

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt, aes(color = maxdepth_class), size = 0.9) +
    # scale_fill_brewer(palette = "Set2") +
    coord_sf(datum = NA) +
    theme_void()

>>>>

```{r 00_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(maxdepth_class = smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, Inf))) %>%
  dplyr::filter(!is.na(maxdepth_class))
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
hu4_focal     <- st_crop(st_transform(
  lwgeom::st_make_valid(hu4_focal), st_crs(study_bbox)), 
  study_bbox)

@@

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt, aes(color = maxdepth_class), size = 0.6, alpha = 0.8) +
    labs(color = "Max depth (m)") +
    # scale_fill_brewer(palette = "Set2") +
    coord_sf(datum = NA) +
    theme_void()
